---
title: "OSBM Staff Survey 2024"
author: "David Yokum"
date: "2024-08-19"
format:
  html: default
server: shiny
---

```{r setup, include=FALSE}
# # Install necessary packages if not already installed
if (!require("readxl")) install.packages("readxl")
if (!require("dplyr")) install.packages("dplyr")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("stringr")) install.packages("stringr")
if (!require("tidyr")) install.packages("tidyr")
if (!require("knitr")) install.packages("knitr")
if (!require("grid")) install.packages("grid")
if (!require("kableExtra")) install.packages("kableExtra")
if (!require("shiny")) install.packages("shiny")
if (!require("plotly")) install.packages("plotly")

# Load the libraries
library(readxl)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(knitr)
library(grid)
library(kableExtra)
library(shiny)
library(plotly)

knitr::opts_chunk$set(echo = TRUE)
```


```{r 2024 Data Import, include=FALSE, warning=FALSE}
# Import data
data <- read_excel("OSBM Employee Satisfaction Survey FY 2024-25(1-56).xlsx")

# Clean column names to remove leading and trailing spaces
colnames(data) <- str_trim(colnames(data))

# Remove trailing (and leading) spaces from the 'Would you re-apply for your job?' column
data <- data %>%
  mutate(`Would you re-apply for your job?` = str_trim(`Would you re-apply for your job?`))

# Random data wrangles
colnames(data)[18] <- "The OSBM Management Team contributes to a positive work culture." 
colnames(data)[20] <- "What are three words that describe OSBMs culture?"
colnames(data)[21] <- "How frequently do you receive recognition from your manager?"
colnames(data)[24] <- "Do you find the allhands meetings valuable?"
colnames(data)[25] <- "How often should allhands meetings be held?"
colnames(data)[26] <- "Do you have any suggestions to improve allhands staff meetings?"
colnames(data)[27] <- "Do you have any recommendations for how to improve the design and management of meetings that you regularly attend?"
colnames(data)[30] <- "Section or Team Meetings"
colnames(data)[31] <- "Informal Conversations with Coworkers"
colnames(data)[39] <- "Which professional development training have you attended?"
colnames(data)[40] <- "Do you feel supported in career progression planning" #"OSBM puts an emphasis on career progression planning and linking that with professional development. Do you feel supported in that regard?" 
colnames(data)[43] <- "What appreciation activities would you be interested in that we have not done?"
colnames(data)[44] <- "This fiscal year, did you utilize lessons and skills learned from OSBMs DEI trainings."
colnames(data)[46] <- "How satisfied are you with OSBMs effort to be culturally diverse and an inclusive work space?" 
colnames(data)[47] <- "What efforts, if any, would increase your satisfaction with OSBMs effort to be culturally diverse and an inclusive work space?" 
colnames(data)[48] <- "How often do you think OSBM should host cultural celebrations?"
colnames(data)[49] <- "Do you have any comments or recommendations about what would increase your satisfaction with the tools you use for work?"

# Data wrangles on factor levels

data <- data %>%
  mutate(`How frequently do you receive recognition from your manager?` = factor(`How frequently do you receive recognition from your manager?`,levels = c("Never", "Monthly", "Weekly", "Daily")))

data <- data %>%
  mutate(`How satisfied are you with OSBMs effort to be culturally diverse and an inclusive work space?` = 
           factor(`How satisfied are you with OSBMs effort to be culturally diverse and an inclusive work space?`, 
                  levels = c("Very dissatisfied", "Somewhat dissatisfied", "Somewhat satisfied", "Very satisfied")))

data <- data %>%
  mutate(`How often do you think OSBM should host cultural celebrations?` = 
           factor(`How often do you think OSBM should host cultural celebrations?`, 
                  levels = c("Monthly", "Quarterly", "Semi-Annually", "Annually")))

```

```{r 2023 data import, echo=FALSE, warning=FALSE}
# Load the 2022-2023 survey data
data_2023 <- read_excel("OSBM Employee Satisfaction Survey FY 2022-23(1-61).xlsx")

# Clean column names for the 2022-2023 data (if necessary)
colnames(data_2023) <- str_trim(colnames(data_2023))

colnames(data_2023)[32] <- "Do you feel supported in career progression planning" #"OSBM puts an emphasis on career progression planning and linking that with professional development. Do you feel supported in that regard?" 
colnames(data_2023)[24] <- "How often should allhands meetings be held?"
```


```{r Set Values, include=FALSE}
osbm_n <-101
total_respondents <- nrow(data)
response_rate <- round(total_respondents / osbm_n * 100, 0)
```

```{r function barchart, echo=FALSE}
barchart <- function(data, question_var, title) {
  
  # Filter out NA values for the specified question variable
  data_filtered <- data %>%
    filter(!is.na(!!sym(question_var)))
  
  # Calculate the total number of responses
  total_responses <- nrow(data_filtered)
  
  # Summarize counts and percentages
  summary_data <- data_filtered %>%
    group_by(!!sym(question_var)) %>%
    summarize(
      count = n(),
      percentage = round((count / total_responses) * 100, 0)
    ) %>%
    complete(!!sym(question_var), fill = list(count = 0, percentage = 0))
  
  # Add custom hover text
  summary_data <- summary_data %>%
    mutate(hover_text = paste0("Count = ", count, "\nPercentage = ", round(percentage, 1), "%"))
  
  # Create the ggplot2 bar chart
  p <- ggplot(summary_data, aes(x = !!sym(question_var), y = percentage, text = hover_text)) +
    geom_bar(stat = "identity", fill = '#0072B2', color = 'black') +
    scale_y_continuous(breaks = seq(0, 100, by = 10),  
                       limits = c(0, 100), 
                       labels = scales::percent_format(scale = 1)) +
    scale_x_discrete(drop = FALSE) +
    labs(title = title, x = NULL, y = "Percentage") +
    theme_minimal()
  
  # Convert to an interactive plotly plot
  p_interactive <- ggplotly(p, tooltip = "text")
  
  # Return the interactive plot
  return(p_interactive)
}
```

```{r function histogram, echo=FALSE}
histogram <- function(data, question_var, title) {
  
  # Filter out NA values and create a clean variable for analysis
  data_combined <- data %>%
    filter(!is.na(!!sym(question_var)))

  # Calculate the overall mean score
  mean_score <- mean(data_combined[[question_var]], na.rm = TRUE)

  # Create the ggplot2 histogram with specific binning
  p_histogram <- ggplot(data_combined, aes(x = !!sym(question_var))) +
    geom_histogram(aes(y = ..density.. * 100),  # Use density for y-axis to avoid stacking
                   binwidth = 1, center = 0.5, fill = '#0072B2', color = 'black') +
    scale_x_continuous(breaks = 0:10, 
                       labels = c("0\nUnhappy", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10\nExtremely Happy"), 
                       limits = c(0, 10)) +
    scale_y_continuous(breaks = seq(0, 100, by = 10),  # Set y-axis notches at 10% intervals
                       limits = c(0, 100), 
                       labels = scales::percent_format(scale = 1)) +
    labs(title = title, x = NULL, y = "Percentage") +
    theme_minimal() +
    geom_vline(xintercept = mean_score, color = "orange", linetype = "solid", linewidth = 1)

  # Convert to an interactive plotly plot with mean line
  p_histogram_interactive <- ggplotly(p_histogram) %>%
    layout(
      hovermode = "closest",
      shapes = list(
        list(
          type = "line",
          x0 = mean_score, x1 = mean_score,
          y0 = 0, y1 = 100,
          line = list(color = 'orange', width = 2)
        )
      ),
      annotations = list(
        list(
          x = mean_score,  # x position at the mean score
          y = 95,  # y position slightly below the top of the plot
          text = paste(" Mean =", round(mean_score, 1)),
          showarrow = FALSE,
          xref = "x",  # Position reference based on x-axis
          yref = "y",  # Position reference based on y-axis
          xanchor = 'left',  # Align text to the left of the position
          font = list(color = "orange", size = 12)  # Customize the label appearance
        )
      )
    )

  # Return the interactive plot
  return(p_histogram_interactive)
}

```

```{r function stacked_bar, echo=FALSE}
stacked_bar <- function(data, questions, title = "Survey Response Distribution") {
  
  # Define the response levels and corresponding colors
  response_levels <- c("Strongly Disagree", "Disagree", "Slightly Disagree", 
                       "Slightly Agree", "Agree", "Strongly Agree")
  
  colors <- c("Strongly Disagree" = "#D73027", "Disagree" = "#FC8D59", 
              "Slightly Disagree" = "#FEE08B", "Slightly Agree" = "#D9EF8B", 
              "Agree" = "#91CF60", "Strongly Agree" = "#1A9850")

  # Ensure the levels are correctly ordered in the data for each question
  data <- data %>%
    mutate(across(all_of(questions), ~ factor(., levels = response_levels)))
  
  # Combine questions into a long format for easier plotting
  plot_data <- data %>%
    select(all_of(questions)) %>%
    pivot_longer(cols = everything(), names_to = "question", values_to = "response")
  
  # Remove NA responses
  plot_data <- na.omit(plot_data)

  # Ensure the response levels are set correctly for proper display
  plot_data$response <- factor(plot_data$response, levels = response_levels)

  # Split the text of questions into two lines
  plot_data$question <- str_wrap(plot_data$question, width = 40)

  # Calculate the counts and ensure all response levels are included
  plot_data <- plot_data %>%
    group_by(question, response) %>%
    summarise(count = n(), .groups = 'drop') %>%
    complete(question, response = response_levels, fill = list(count = 0))

  # Calculate the total count for each question
  plot_data <- plot_data %>%
    group_by(question) %>%
    mutate(total_count = sum(count)) %>%
    ungroup()

  # Calculate the proportions within each question
  plot_data <- plot_data %>%
    mutate(prop = count / total_count)

  # Correct the positions for the diverging bars with the correct order
  plot_data <- plot_data %>%
    mutate(
      response_position = case_when(
        response == "Strongly Disagree" ~ -prop,
        response == "Disagree" ~ -prop,
        response == "Slightly Disagree" ~ -prop,
        response == "Slightly Agree" ~ prop,
        response == "Agree" ~ prop,
        response == "Strongly Agree" ~ prop
      )
    )

  # Adjust the order of levels for plotting
  plot_data$response <- factor(plot_data$response, levels = c("Strongly Disagree", "Disagree", "Slightly Disagree",
                                                              "Strongly Agree", "Agree", "Slightly Agree"))

  # Create the diverging stacked bar chart
  p <- ggplot(plot_data, aes(x = question, y = response_position, fill = response, 
                             text = paste0("Count: ", count, "\nProportion: ", scales::percent(prop)))) +
    geom_bar(stat = "identity", width = 0.7) +  # Increase bar width
    scale_y_continuous(breaks = seq(-1, 1, by = 0.5),  # Set y-axis (flipped x-axis) notches at 20% intervals
                       labels = scales::percent_format(scale = 100), 
                       limits = c(-1, 1)) +
    scale_fill_manual(values = colors) +
    labs(title = title, x = NULL, y = "Percentage", fill = "Response") +
    coord_flip() +
    theme_minimal()

  # Convert to an interactive plotly plot with a single-line legend and simplified theme
  p_interactive <- ggplotly(p, tooltip = "text") %>%
    layout(
      yaxis = list(title = NULL),
      xaxis = list(title = "Percentage", tickformat = "%"),
      margin = list(t = 200, b = 50, l = 50, r = 50),  # Increase the top margin for the legend
      legend = list(
        orientation = "h",  # Horizontal orientation
        x = 0.25,  # Center the legend horizontally
        y = 1.1,  # Move the legend further above the plot area
        xanchor = "center",
        yanchor = "bottom",
        font = list(
          size = 8  # Reduce the legend text size to fit on one line
        ),
        title = list(text = ""),  # Remove the legend title
        itemwidth = 0  # Optional: adjust item width to prevent text wrapping
      )
    )
  
  return(p_interactive)
}

# # Example usage:
# stacked_bar(data, questions = c("As an OSBM employee, I have a clear understanding of my career or promotion path.",
#                                 "I feel valued at work.",
#                                 "I'll be able to reach my full potential at OSBM."),
#             title = "Title")

```

```{r function why_answer, echo=FALSE}

why_answer <- function(data, filter_var = NULL, response_var, app_title = "") {
  
  # Define the UI
  ui <- fluidPage(
    
    # Application title
    titlePanel(app_title),
    
    # Sidebar layout with input and output definitions
    sidebarLayout(
      sidebarPanel(
        # Add custom CSS to fix the sidebar in place
        tags$head(tags$style(HTML("
          .fixed-sidebar {
            position: fixed;
            width: 250px;
            top: 60px;
            background-color: #f8f9fa;
            padding-right: 15px;
            height: 100%;
            overflow-y: auto;
            z-index: 1000;
          }
          .main-panel-adjust {
            margin-left: 270px;
            padding-left: 15px;
          }
          .shiny-bound-output {
            margin-top: 20px;
          }
          .sticky-table-header {
            overflow-y: auto;
            height: 500px;
            border: 1px solid #ddd;
          }
          .sticky-table-header table {
            border-collapse: collapse;
            width: 100%;
            table-layout: fixed;
          }
          .sticky-table-header thead th {
            position: sticky;
            top: 0;
            background: white;
            z-index: 1000;
            border-bottom: 1px solid #ddd;
          }
        "))),
        
        # Apply the fixed-sidebar class to the panel
        div(class = "fixed-sidebar",
            # Conditional panel for filter input if filter_var is provided
            conditionalPanel(
              condition = "input.filter_var !== ''",
              selectInput("referral_answer", paste("", filter_var), 
                          choices = c("Yes", "No"))
            )
        )
      ),
      
      mainPanel(
        class = "main-panel-adjust",  # Adjust the main panel to avoid overlap with the fixed sidebar
        # Output the table as HTML with a sticky header
        div(class = "sticky-table-header",
            htmlOutput("feedback_table"))
      )
    )
  )
  
  # Define the server logic
  server <- function(input, output) {
    
    # Create the reactive data based on the selected referral answer
    filtered_data <- reactive({
      if (!is.null(filter_var) && filter_var != "") {
        data %>%
          filter(!!sym(filter_var) == input$referral_answer) %>%
          select(!!sym(response_var))
      } else {
        data %>%
          select(!!sym(response_var))
      }
    })
    
    # Render the table as kable
    output$feedback_table <- renderUI({
      table_data <- filtered_data()
      
      # Check if there's any data to display
      if(nrow(table_data) == 0) {
        return(h4("No responses found for the selected option."))
      }
      
      # Generate the kable table as HTML with a sticky header
      table_output <- kable(table_data, col.names = NULL, format = "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, position = "left") %>%
        add_header_above(header = c(paste("Why or why not?")),
                         bold = TRUE, font_size = 14, color = "black", background = "white") %>%
        row_spec(0, bold = TRUE, font_size = 18, align = "1", extra_css = "background-color: white; border-bottom: none;")
      
      HTML(table_output)
    })
  }
  
  # Run the application 
  shinyApp(ui = ui, server = server)
}



# # Example usage:
# why_answer(
#   data = data, 
#   filter_var = "Would you refer someone to work here?", 
#   response_var = "If you would refer someone to work at OSBM, why? If not, why not?"
# )

```


```{r function responses, echo=FALSE}
responses <- function(data, response_var, app_title = "") {
  
  # Define the UI
  ui <- fluidPage(
    
    # Application title
    titlePanel(app_title),
    
    # Main layout with output
    mainPanel(
      # Apply custom CSS to make the table header sticky
      tags$head(tags$style(HTML("
        .sticky-table-header {
          overflow-y: auto;
          height: 500px;
          border: 1px solid #ddd;
        }
        .sticky-table-header table {
          border-collapse: collapse;
          width: 100%;
          table-layout: fixed;
        }
        .sticky-table-header thead th {
          position: sticky;
          top: 0;
          background: white;
          z-index: 1000;
          border-bottom: 1px solid #ddd;
        }
      "))),
      
      # Output the table as HTML with a sticky header
      div(class = "sticky-table-header",
          htmlOutput("response_table"))
    )
  )
  
  # Define the server logic
  server <- function(input, output) {
    
    # Create the reactive data to hold all responses for the specified variable
    all_responses <- reactive({
      data %>%
        select(!!sym(response_var))
    })
    
    # Render the table as kable
    output$response_table <- renderUI({
      table_data <- all_responses()
      
      # Check if there's any data to display
      if(nrow(table_data) == 0) {
        return(h4("No responses found for this variable."))
      }
      
      # Generate the kable table as HTML with a sticky header
      table_output <- kable(table_data, col.names = NULL, format = "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, position = "left") %>%
        add_header_above(header = c(paste("", response_var)),
                         bold = TRUE, font_size = 14, color = "black", background = "white") %>%
        row_spec(0, bold = TRUE, font_size = 18, align = "1", extra_css = "background-color: white; border-bottom: none;")
      
      HTML(table_output)
    })
  }
  
  # Run the application 
  shinyApp(ui = ui, server = server)
}


# # Example
# responses(
#   data = data, 
#   response_var = "If you would refer someone to work at OSBM, why? If not, why not?", 
#   app_title = "All Responses"
# )
```

```{r histogram overlay, echo=FALSE}

histogram_overlay <- function(data1, data2, var1, var2, title) {
  
  # Filter out NA values and create clean variables for analysis
  data_combined_1 <- data1 %>%
    filter(!is.na(!!sym(var1)))
  
  data_combined_2 <- data2 %>%
    filter(!is.na(!!sym(var2)))
  
  # Calculate the overall mean scores for both datasets
  mean_score_1 <- mean(data_combined_1[[var1]], na.rm = TRUE)
  mean_score_2 <- mean(data_combined_2[[var2]], na.rm = TRUE)
  
  # Calculate the counts and percentages for hover text
  summary_data_1 <- data_combined_1 %>%
    group_by(!!sym(var1)) %>%
    summarize(
      count = n(),
      percentage = round((count / nrow(data_combined_1)) * 100, 0)
    )
  
  summary_data_2 <- data_combined_2 %>%
    group_by(!!sym(var2)) %>%
    summarize(
      count = n(),
      percentage = round((count / nrow(data_combined_2)) * 100, 0)
    )
  
  # Add hover text based on correct percentages
  data_combined_1 <- data_combined_1 %>%
    left_join(summary_data_1, by = setNames(var1, var1)) %>%
    mutate(hover_text = paste0("Count = ", count, "\nPercentage = ", round(percentage, 1), "%"))
  
  data_combined_2 <- data_combined_2 %>%
    left_join(summary_data_2, by = setNames(var2, var2)) %>%
    mutate(hover_text = paste0("Count = ", count, "\nPercentage = ", round(percentage, 1), "%"))
  
  # Create the ggplot2 histogram for the 2024-2025 data
  p_histogram <- ggplot(data_combined_1, aes(x = !!sym(var1), text = hover_text)) +
    geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100), 
                   binwidth = 1, center = 0.5, fill = '#0072B2', color = 'black', alpha = 0.7) +
    geom_histogram(data = data_combined_2, aes(x = !!sym(var2), y = after_stat(count) / sum(after_stat(count)) * 100), 
                   binwidth = 1, center = 0.5, fill = 'grey', color = 'black', alpha = 0.3) +
    scale_x_continuous(breaks = 0:10, 
                       labels = c("0\nUnhappy", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10\nExtremely Happy"), 
                       limits = c(0, 10)) +
    scale_y_continuous(breaks = seq(0, 100, by = 10),  # Set y-axis notches at 10% intervals
                       limits = c(0, 100), 
                       labels = scales::percent_format(scale = 1)) +
    labs(title = title, x = NULL, y = "Percentage") +
    theme_minimal() +
    geom_vline(xintercept = mean_score_1, color = "orange", linetype = "solid", linewidth = 1) +
    geom_vline(xintercept = mean_score_2, color = "grey", linetype = "dashed", linewidth = 1)
  
  # Convert to an interactive plotly plot with custom hover text and mean lines
  p_histogram_interactive <- ggplotly(p_histogram, tooltip = "text") %>%
    layout(
      hovermode = "closest",
      shapes = list(
        list(
          type = "line",
          x0 = mean_score_1, x1 = mean_score_1,
          y0 = 0, y1 = 100,
          line = list(color = 'orange', width = 2)
        ),
        list(
          type = "line",
          x0 = mean_score_2, x1 = mean_score_2,
          y0 = 0, y1 = 100,
          line = list(color = 'grey', width = 2, dash = 'dash')
        )
      ),
      annotations = list(
        list(
          x = mean_score_1,  # x position at the mean score for 2024-25
          y = 95,  # y position slightly below the top of the plot
          text = paste("2024-25 Mean =", round(mean_score_1, 1)),
          showarrow = FALSE,
          xref = "x",  # Position reference based on x-axis
          yref = "y",  # Position reference based on y-axis
          xanchor = 'left',  # Align text to the left of the position
          font = list(color = "orange", size = 12)  # Customize the label appearance
        ),
        list(
          x = mean_score_2,  # x position at the mean score for 2022-23
          y = 85,  # y position slightly below the mean label for 2024-25
          text = paste("2022-23 Mean =", round(mean_score_2, 1)),
          showarrow = FALSE,
          xref = "x",  # Position reference based on x-axis
          yref = "y",  # Position reference based on y-axis
          xanchor = 'left',  # Align text to the left of the position
          font = list(color = "grey", size = 12)  # Customize the label appearance
        )
      )
    )
  
  # Return the interactive plot
  return(p_histogram_interactive)
}

# Example Usage
# histogram_overlay(data, data_2023, 
#                   var1 = "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?", 
#                   var2 = "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?", 
#                   title = "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?")
```

```{r function overlay barchart, echo=FALSE}
overlay_barchart <- function(data1, data2, var1, var2, title) {
  
  # Summarize data1
  summary_data1 <- data1 %>%
    filter(!is.na(!!sym(var1))) %>%
    group_by(!!sym(var1)) %>%
    summarize(
      count = n(),
      percentage = round((count / sum(count)) * 100, 1)
    )
  
  # Summarize data2
  summary_data2 <- data2 %>%
    filter(!is.na(!!sym(var2))) %>%
    group_by(!!sym(var2)) %>%
    summarize(
      count = n(),
      percentage = round((count / sum(count)) * 100, 1)
    )
  
  # Combine the summarized data into one dataframe
  combined_data <- full_join(
    summary_data1 %>% rename(Percentage1 = percentage),
    summary_data2 %>% rename(Percentage2 = percentage),
    by = setNames(var1, var2)
  )
  
  # Reshape the data for easier plotting with ggplot2
  plot_data <- combined_data %>%
    gather(key = "Dataset", value = "Percentage", -!!sym(var1)) %>%
    mutate(Dataset = factor(Dataset, levels = c("Percentage1", "Percentage2")))
  
  # Create the overlay bar chart using ggplot2
  p <- ggplot(plot_data, aes_string(x = var1, y = "Percentage", fill = "Dataset", text = "Percentage")) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    scale_fill_manual(values = c("Percentage1" = "#0072B2", "Percentage2" = "grey")) +
    labs(title = title, x = NULL, y = "Percentage") +
    theme_minimal()
  
  # Convert the ggplot2 plot to an interactive plotly plot
  p_interactive <- ggplotly(p, tooltip = "text")
  
  # Return the interactive plot
  return(p_interactive)
}

# # Example Usage
# overlay_barchart(
#   data1 = data, 
#   data2 = data_2023, 
#   var1 = "Would you refer someone to work here?", 
#   var2 = "Would you refer someone to work here?", 
#   title = "Overlay of Responses: Would you refer someone to work here?"

```

## About

In July 2024, `r total_respondents` of `r osbm_n` OSBM employees (affiliates included) completed the annual employee satisfaction survey - a response rate of `r response_rate`%. 

## Employee Satisfaction

```{r Happiness histogram, echo=FALSE, warning=FALSE}
histogram(data, "On a scale of 1 to 10, how happy are you at work?", "Fig 1. On a scale of 0 to 10, how happy are you at work?")
```

```{r Referral, echo=FALSE}
barchart(data, "Would you refer someone to work here?", "Fig 2. Would you refer someone to work here?")
```

```{r Why refer, echo=FALSE}
why_answer(
  data = data, 
  filter_var = "Would you refer someone to work here?", 
  response_var = "If you would refer someone to work at OSBM, why? If not, why not?"
)
```

```{r echo=FALSE}
stacked_bar(data, questions = c("As an OSBM employee, I have a clear understanding of my career or promotion path.",
                                "I feel valued at work.",
                                "I'll be able to reach my full potential at OSBM.",
                                "If given the chance, I would reapply to my current job.",
                                "If given the chance, I would reapply to my current job."),
            title = "Fig 3. Employee Sentiment")
```

```{r echo=FALSE}
barchart(data, "Would you re-apply for your job?", "Fig 4. Would you re-apply for your job?")
```

```{r Why repply, echo=FALSE}
why_answer(
  data = data, 
  filter_var = "Would you re-apply for your job?",
  response_var = "Why or why not? Expanding on the answer to Question 5."
)
```

```{r working here, echo=FALSE}
barchart(data, "Please complete this statement: I see myself working here...", "Fig 5. I see myself working here...")
```

## Organizational Culture

```{r org culture - likert, echo=FALSE}
stacked_bar(data, questions = c("My OSBM coworkers respect each other.",
                                "I feel respected as an employee at OSBM.",
                                "The OSBM Management Team contributes to a positive work culture.",
                                "I know what OSBMs mission and vision are."),
            title = "Fig 6. Employee Sentiment")
```


```{r three words, echo=FALSE}
responses(data, response_var = "What are three words that describe OSBMs culture?", "What are three words that describe OSBM's culture?")
```

```{r freq praise, echo=FALSE}
barchart(data, "How frequently do you receive recognition from your manager?", "Fig 7. How frequently do you receive recognition from your manager?")
```

```{r praise last project, echo=FALSE}
barchart(data, "The last time you accomplished a big project, did you receive any recognition?", "Fig 8. The last time you accomplished a big project, did you receive any recognition?")
```

```{r comfort, echo=FALSE}
histogram(data, "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?", "Fig 9. How comfortable do you feel giving feedback to your manager?")
```

## Officewide Communication

```{r all-hands valuable, echo=FALSE}
barchart(data, "Do you find the allhands meetings valuable?", "Fig 10. Do you find the all-hands meetings valuable?")
```

```{r freq all hands, echo=FALSE}
barchart(data, "How often should allhands meetings be held?", "Fig 11. How often should all-hands meetings be held?")
```

```{r}
barchart(data_2023, "How often should allhands meetings be held?", "Fig 11_2023. How often should all-hands meetings be held?")

```


```{r improve all-hands, echo=FALSE}
responses(data, response_var = "Do you have any suggestions to improve allhands staff meetings?")
```

```{r improve other mtgs, echo=FALSE}
responses(data, response_var = "Do you have any recommendations for how to improve the design and management of meetings that you regularly attend?")
```


```{r going on, echo=FALSE}
stacked_bar(data, questions = c("I know what is going on across the office."),
            title = "Fig 12. Employee Sentiment")
```

```{r osbm info sources, echo=FALSE}
stacked_bar(data, questions = c("All Hands Staff Meetings", 
                                "Section or Team Meetings", 
                                "Informal Conversations with Coworkers",
                                "Monthly OSBM Email Newsletter",
                                "OSBM Website",
                                "OSBM Intranet Site",
                                "Individual Meetings with your Supervisor",
                                "OSBM LinkedIn Account"
                                ),
            title = "Fig 13. Please provide your sentiment towards the importance of the sources that you rely on for OSBM information and its activities")

```

```{r recs to improve comms, echo=FALSE}
responses(data, response_var = "Do you have suggestions on how to improve communications?")
```

## Professsional Development

```{r prof dev, echo=FALSE}
barchart(data, "In the past 12 months, have you attended any professional development trainings?", "Attended professional development trainings in past 12 months?")

responses(data, response_var = "Which professional development training have you attended?")
```

```{r career progression, echo=FALSE}
barchart(data, "Do you feel supported in career progression planning", "Fig 16. Do you feel supported in career progression planning?")
```

```{r coworker interact, echo=FALSE}
barchart(data, "In which setting do you like to interact with your coworkers for events?", "Fig 17. In which setting do you like to interact with your coworkers for events?")

responses(data, "For the events that you have participated in, would you change anything about that activity?")

responses(data, "What appreciation activities would you be interested in that we have not done?")
```

## Diversity, Equity, and Inclusion

```{r utilize DEI, echo=FALSE}
barchart(data, "This fiscal year, did you utilize lessons and skills learned from OSBMs DEI trainings.", "Fig 18. Did you use lessons & skills learned from OSBM's DEI trainings?")

stacked_bar(data, questions = c("OSBM appropriately celebrates diversity through events and celebrations."),
            title = "Fig 19. Employee Sentiment")

barchart(data, "How satisfied are you with OSBMs effort to be culturally diverse and an inclusive work space?", "How satisfied w/ OSBM's efforts to be culturally diverse & inclusive?")

responses(data, "What efforts, if any, would increase your satisfaction with OSBMs effort to be culturally diverse and an inclusive work space?")

barchart(data, "How often do you think OSBM should host cultural celebrations?", "Fig 21. How often should OSBM host cultural celebrations?")
```

## General Feedback

```{r general feedback, echo=FALSE}

responses(data, "Do you have any comments or recommendations about what would increase your satisfaction with the tools you use for work?")

responses(data, "Do you have any comments or recommendations about what would increase your satisfaction with your calendar and telework flexibilities?")

responses(data, "Overall, how competitive do you feel OSBM is in terms of employee compensation, opportunities and employee appreciation compared to other agencies?")

responses(data, "Do you have any comments or thoughts about the OSBM relocation effort to the Old Revenue Building or the new office/building facilities?")

responses(data,"Do you have any questions, concerns, or suggestions about the upcoming Governors transition?")

responses(data,"Please feel free to leave any comments, questions, or concerns as it relates to employee satisfaction at OSBM.")

```

## Word Cloud

```{r echo=FALSE}
# Install necessary packages if not already installed
if (!require("tm")) install.packages("tm")
if (!require("wordcloud2")) install.packages("wordcloud2")

library(tm)
library(wordcloud2)

# List of words (your provided list)
words <- c(
  "Dedicated, trustworthy, thoughtful",
  "collaborative, motivating, flexible",
  "innovative, good values, inclusive",
  "overloaded isolated professionals",
  "Friendly, comfortable, goal-oriented",
  "collaborative, innovate, chill",
  "inclusive, flexible, open",
  "Dedicated, curious, analytical",
  "inclusive, motivating, intellectual",
  "positive, driven, creative",
  "positive, modern, appreciative",
  "Positive, encouraging, and enthusiastic.",
  "dedicated, thorough, inclusive.",
  "Supportive, kind, driven",
  "inclusive, motivating, empowering",
  "Flexible/Fun/Diverse",
  "curiosity, collaborative and focused",
  "Collaborative, Smart, Fast Paced",
  "Flexible, Friendly, Dedicated",
  "Flexible, focused, friendly",
  "friendly, collaborative, inviting",
  "honest, knowledgeable, friendly",
  "Positive, Professional, Unbalanced",
  "Collaborative, Curious, Nerdy",
  "Collegial, thoughtful, supportive",
  "Supportive, Family, Opportunity",
  "team-oriented, respectful, innovative",
  "mission-focused, honest, ambitious",
  "Professional, flexible, cooperative",
  "curious, supportive, shared accountability",
  "Supportive, respectful, public service",
  "Collaborative, dedicated, professional",
  "Curious, intelligent, dedicated",
  "Hectic, Professional, Overwhelmed",
  "professional, respectful, dedicated",
  "collaborative, supportive, hard working",
  "Calm, Organized, Direct",
  "N/A",
  "professional relaxed friendly",
  "Positive, Open, Adaptive",
  "Diverse, Collaboration, Accountability",
  "Supportive Impactful Committed",
  "team building, support, work life balance",
  "focused, fun, friendly",
  "friendly, flexible, collaborative",
  "Professional, expert, proactive",
  "Supportive, Flexible and Kind",
  "Motivating, family environment, collaborative",
  "Collaborative, Supportive and Curious",
  "Professional, supportive, positive",
  "welcoming, engaging, meaningful",
  "Positive, Inspiring, and Challenging"
)

# Convert to a single string
words_combined <- paste(words, collapse = " ")

# Convert to lowercase and split into individual words
word_list <- tolower(unlist(strsplit(words_combined, "\\W+")))

# Remove common stop words (optional)
word_list <- removeWords(word_list, stopwords("en"))

# Generate the word cloud
word_freq <- table(word_list)
wordcloud2(data.frame(word = names(word_freq), freq = as.numeric(word_freq)),
           size = 1, color = "random-light", backgroundColor = "white")

```


```{r comfort histogram overlay, echo=FALSE, include=FALSE}
histogram_overlay(data, data_2023,
                  var1 = "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?",
                  var2 = "On a scale of 1 to 10, how comfortable do you feel giving feedback to your manager?",
                  title = "How comfortable do you feel giving feedback to your manager?")
```

```{r career planning histogram overlay, echo=FALSE}
# histogram_overlay(data, data_2023,
#                   var1 = "Do you feel supported in career progression planning",
#                   var2 = "Do you feel supported in career progression planning",
#                   title = "How comfortable do you feel giving feedback to your manager?")
```

### Decision Points

1. Should the all staff meeting be bi-monthly?
2. Should we jettison or revamp the ASBO 2-min reports during all staff? 
2. Should a 3rd telework day be considered? 
4. Should there be more frequent telework weeks (e.g. around holidays)?
5. Should the OSBM newsletter include more inward facing content (or even a staff newsletter)?
6. KW you're talking about transition tomorrow, yes? 
7. Lot of these stats feed into strat plan - how to sync w/ strat plan update?
